The imprint of global magma oceans on exoplanet demographics

### 2022-12-01 src/tex/ms.tex
describe MO injection with Bioverse; introduce the three structure cases

\section{Testing the magma ocean hypothesis}
\todo[inline]{Methods and results section of the hypothesis testing part. Introduce the idea of constraining magma ocean frequencies and/or physics with Bayesian stats on exoplanet population; introduce Bioverse; report methods of the hypothesis tests.}
The purpose of this paper is to demonstrate the feasibility of measuring the demographic feature introduced above with near-future exoplanet missions.
This section describes our approach.

@@

\subsection{Synthetic planet sample}
Next, we assigned planetary systems to the synthetic stellar sample.
The orbital parameters and bulk properties of these simulated planets are informed by statistics from the \kepler\ mission.

@@

\subsubsection{Synthetic planet populations with and without magma oceans}
\todo{describe the way we inject magma oceans into the synthetic planet population with Bioverse}
\begin{note}

@@

%\begin{acknowledgments}
%The authors thank Yann Fabel, Paul Molliere, and Terry-Ann Suer for insightful discussions.
%We are grateful to Martin Turbet for providing the mass-radius relationship data.
%\end{acknowledgements}

>>>>

\section{Testing the magma ocean hypothesis}
\todo[inline]{Methods and results section of the hypothesis testing part. Introduce the idea of constraining magma ocean frequencies and/or physics with Bayesian stats on exoplanet population; introduce Bioverse; report methods of the hypothesis tests.\\
Caveats: see \citet{Turbet2019} Sect. 3, \citet{Bower2019}}
The purpose of this paper is to demonstrate the feasibility of measuring the demographic feature introduced above with near-future exoplanet missions.
This section describes our approach.

@@

\subsection{Synthetic planet sample}\label{sec:syn_planets}
Next, we assigned planetary systems to the synthetic stellar sample.
The orbital parameters and bulk properties of these simulated planets are informed by statistics from the \kepler\ mission.

@@

\subsubsection{Synthetic planet populations with and without magma oceans}
\todo{describe the way we inject magma oceans into the synthetic planet population with Bioverse}
\begin{note}
    Central to our procedure is to explore the detectability of population-level trends with future exoplanet surveys, and here the trend in question is the proposed radius discontinuity.
    To enable a quantitative assessment of this detectability, we injected the signal into the simulated planet sample before observing it with simulated surveys.
    While we search for the magma ocean pattern in demographic quantities such as average planet radii, the injected changes happen on the planetary level: We changed each planet's radius based on its individual set of properties and the associated predictions from steam atmosphere and water incorporation models.
    Relevant properties are a planet's mass $M$, its instellation $S$, and its bulk water inventory expressed as a water mass fraction $x_{H_2O}$.
    We consider three different cases:
    \begin{itemize}
   \item[A.] No radius change.
    This case serves as our null hypothesis, where planetary radii are not affected by the amount of irradiation the planets receive.
    It also applies outside the runaway greenhouse limit, where we assume a solid planetary surface and no steam atmosphere.
        A planet that lies \textit{within} the runaway greenhouse limit but that is already completely desiccated will have the same radius. \todo{Mention if this case is considered in the model or not (as of now, no).}
   \item[B.] Radius inflation due to a steam atmosphere.
    We assigned planets within the runaway greenhouse limit steam atmospheres, which increase atmospheric scale heights significantly.
   \item[C.] Radius decrease of inflated planets due to water in the melt.
    Due to greenhouse forcing, planetary surfaces below steam atmospheres are thought to be molten.
    Part of the water will then partition into the melt, removing it from the steam atmosphere, which in turn decreases the radius inflation.
    This effect is generally small compared to the radius inflation from a steam atmosphere but resulting radius changes typically reach measurable values.
    \end{itemize}
\end{note}

In case A, a planet simply retains the radius it was assigned based on exoplanet occurrence rates (see Sect.~\ref{sec:syn_planets}).
Case B assumes an inflated radius due to a steam atmosphere for runaway greenhouse planets.
To quantify this radius change, we applied the mass-radius relationships derived by \citet{Turbet2020} using a 1D~inverse radiative-convective model~\citep{Turbet2019}.
Their calculations start from the same underlying mass-radius relations that we use for case-A-planets~\citep{Zeng2016}.
...

@@

%\begin{acknowledgments}
%The authors thank Yann Fabel, Paul Molliere, and Terry-Ann Suer for insightful discussions.
%We are grateful to Martin Turbet for providing the mass-radius relationship data for planets harboring steam atmospheres.
%\end{acknowledgements}
